How to compute the fusion product of MV cycles in type A

### 2021-02-21 draft.tex
circ contained in not equal to central fibre of bdgr typo

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) = \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
% \jcom{Now answered above.}

>>>>

We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $ X_1 \times X_2 \times \AA^\times $ inside of $ \Grbd $.  
We use the projection $ \pi: \Grbd \rightarrow \AA $ to form $ X_1 \circ X_2 = (X_1 \ast_\AA X_2) \cap \pi^{-1}(0) \subset \Gr_{0,0} $, which we call the fusion of $ X_1 $ and $X_2$.  
We regard $ X_1 \circ X_2$ as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $. 
% \acom{Repeat question: what is this iso? Roger says maybe it's in MV?}
% \jcom{Now answered above.}
